Benchmarks

### 2012-10-24 docs/roadmap/benchmarks.tex
Pre splitting rework.

% --------------------------------------------------------------------------------
\subsubsection*{Intermediate results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(ms) & \bf T(ms) & \bf P(ms) \\ \midrule
1024 & 32 & CPU baseline & 1965.63 & 1191.13 & 6069.66 \\
1024 & 32 & GPU baseline & 838.67 & 499.87 & 516.82 \\
1024 & 32 & GPU sync improved & 642.37 & 316.40 & 343.29 \\
2048 & 32 & CPU baseline & 27229.28 & 15296.09 & 57323.04 \\
2048 & 32 & GPU P 32 blocks & 2864.27 & 1427.21 & 2096.34 \\
\bottomrule \end{tabular} \\[4pt]
Best timings for R=rectangle, T=triangle, P=parallelogram\footnote{$\le 32$ blocks on my GPU to prevent deadlock}
\end{center}

>>>>

% --------------------------------------------------------------------------------
\subsubsection*{Intermediate results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(ms) & \bf T(ms) & \bf P(ms) \\ \midrule
1024 & 32 & CPU baseline & 1965.63 & 1191.13 & 6069.66 \\
1024 & 32 & GPU baseline & 838.67 & 499.87 & 516.82 \\
1024 & 32 & GPU sync improved & 642.37 & 316.40 & 343.29 \\
2048 & 32 & CPU baseline & 27229.28 & 15296.09 & 57323.04 \\
2048 & 32 & GPU P $\le32$ blocks & 2864.27 & 1427.21 & 2096.34 \\
4096 & 32 & GPU 8 splits & & & 16767.58 \\
8192 & 32 & GPU 64 splits & & & 135793.22 \\
12288 & 32 & GPU 256 splits & & & 460912.44 \\

\bottomrule \end{tabular} \\[4pt]
Best timings for R=rectangle, T=triangle, P=parallelogram\footnote{$\le 32$ blocks on my GPU to prevent deadlock}
\end{center}
